\documentclass{sig-alternate-05-2015}


\begin{document}

\setcopyright{acmcopyright}

\conferenceinfo{FSE '16}{November 13--19, 2016, Seattle, WA, USA}


\title{A Doomsday Vault of Software Engineering Tools}
\subtitle{Archiving Software Engineering Tools from ICSE and FSE 2011 through 2014}

\numberofauthors{75}

\author{
\alignauthor
Emerson Murphy-Hill\\
       \affaddr{Department of Computer Science}\\
       \affaddr{NC State University}\\
       \affaddr{Raleigh, NC, USA 27695}\\
       \email{emerson@csc.ncsu.edu}}

\additionalauthors{Additional authors: 
%Example:
% John Smith (The Th{\o}rv{\"a}ld Group,
% email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
% (The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).
%Alphabetical:
Shabbir Abdul (\url{sabdul@ncsu.edu}), 
Varun Aettapu (\url{vaettap@ncsu.edu}), 
Sumeet Agarwal (\url{sagarwa6@ncsu.edu}), 
Sindhu Anangur Vairavel (\url{sanangu@ncsu.edu}), 
Rishi Avinash Anne (\url{raanne@ncsu.edu}), 
Haris Mahmood Ansari (\url{hmansari@ncsu.edu}), 
Ankit Bhandari (\url{abhanda3@ncsu.edu}), 
Anand Bhanu (\url{bhanua@ncsu.edu}), 
Aditya Vinayak Bhise (\url{avbhise@ncsu.edu}), 
Saikrishna Teja Bobba (\url{sbobba3@ncsu.edu}), 
Vineela Boddula (\url{vboddul@ncsu.edu}), 
Venkata Krishna Sailesh Bommisetti (\url{vbommis@ncsu.edu}), 
Dwayne Christian (Chris) Brown (\url{dcbrow10@ncsu.edu}), 
Peter Morgan Chen (\url{pmchen@ncsu.edu}), 
Yi Chun (\url{Yi-Chun}) Chen (\url{ychen74@ncsu.edu}), 
Nikhil Chinthapallee (\url{nchinth@ncsu.edu}), 
Karan Singh Dagar (\url{kdagar@ncsu.edu}), 
Joseph Decker (\url{jdecker@ncsu.edu}), 
Pankti Rakeshkumar Desai (\url{prdesai2@ncsu.edu}), 
Jayant Dhawan (\url{jdhawan2@ncsu.edu}), 
Yihuan Dong (\url{ydong2@ncsu.edu}),
Sarah Elizabeth Elder (\url{seelder@ncsu.edu}), 
Shrenuj Gunvant Gandhi (\url{sgandhi4@ncsu.edu}), 
Jennifer Michelle Green (\url{jmgree17@ncsu.edu}), 
Mohammed Hasibul Hassan (\url{mhhassan@ncsu.edu}), 
Satish Inampudi (\url{sinampu@ncsu.edu}), 
Pragyan Paramita Jena (\url{ppjena@ncsu.edu}), 
Bhargav Rahul (\url{Bhargav}) Jhaveri (\url{bjhaver@ncsu.edu}), 
Apoorv Vijay Joshi (\url{avjoshi@ncsu.edu}), 
Nikhil Josyabhatla (\url{njosyab@ncsu.edu}), 
Sujith Katakam (\url{skataka@ncsu.edu}), 
Juzer Husainy Khambaty (\url{jhkhamba@ncsu.edu}), 
Aneesh Arvind Kher (\url{aakher@ncsu.edu}), 
Craig Kimpel (\url{ckimpal@ncsu.edu}), 
Siddhartha Kollipara (\url{skollip@ncsu.edu}), 
Asish Prabhakar Kottala (\url{akottal@ncsu.edu}), 
Abishek Kumar (\url{akumar21@ncsu.edu}), 
Harini Reddy Kumbum (\url{hkumbum@ncsu.edu}), 
Nitish Pradeep Limaye (\url{nplimaye@ncsu.edu}), 
Apoorv Mahajan (\url{amahaja3@ncsu.edu}), 
Sai Sindhur Malleni (\url{smallen3@ncsu.edu}), 
Sudha Manchukonda (\url{smanchu@ncsu.edu}), 
Kavit Maral Mehta (\url{kmmehta@ncsu.edu}), 
Justin Alan Middleton (\url{jamiddl2@ncsu.edu}), 
Ramakant Moka (\url{rmoka@ncsu.edu}), 
Eesha Gopalakrishna Mulky (\url{egmulky@ncsu.edu}), 
Gauri Naik (\url{gnaik2@ncsu.edu}), 
Shraddha Anil Naik (\url{sanaik2@ncsu.edu}), 
Yashwanth Nallabothu (\url{ynallab@ncsu.edu}), 
Yogesh Nandakumar (\url{ynandak@ncsu.edu}), 
Kairav Sai Padarthy (\url{kspadart@ncsu.edu}), 
Pulkesh Kumar Yadav Pannalal (\url{ppannal@ncsu.edu}), 
Sattwik Pati (\url{spati2@ncsu.edu}), 
Kahan Prabhu (\url{kprabhu@ncsu.edu}), 
Shashank Goud Pulimamidi (\url{spulima@ncsu.edu}), 
Gargi Sandeep Rajadhyaksha (\url{gsrajadh@ncsu.edu}), 
Priyadarshini Rajagopal (\url{prajago4@ncsu.edu}), 
Venkatesh Sambandamoorthy (\url{vsamban@ncsu.edu}), 
Mohan Sammeta (\url{msammet@ncsu.edu}), 
Shaown Sarker (\url{ssarker@ncsu.edu}), 
Anshita Sayal (\url{asayal@ncsu.edu}), 
Vrushti Kamleshkumar Shah (\url{vkshah@ncsu.edu}), 
Esha Sharma (\url{esharma2@ncsu.edu}), 
Saurav Shekhar (\url{sshekha3@ncsu.edu}), 
Sarthak Prabhakar Shetty (\url{spshetty@ncsu.edu}), 
Manish Ramashankar Singh (\url{mrsingh@ncsu.edu}), 
Ankush Kumar Singh (\url{asingh21@ncsu.edu}), 
Vinay Kumar Suryadevara (\url{vksuryad@ncsu.edu}), 
Sumit Kumar Tomer (\url{sktomer@ncsu.edu}), 
Akriti Tripathi (\url{atripat4@ncsu.edu}), 
Jennifer Tsan (\url{jtsan@ncsu.edu}), 
Vivekananda Vakkalanka (\url{vvakkal@ncsu.edu}), 
Alexander Valkovsky (\url{avalkov@ncsu.edu}), 
Rishi Kumar Vardhineni (\url{rkvardhi@ncsu.edu}) and
Manav Verma (\url{mverma4@ncsu.edu}).}
%\date{30 July 1999}

\maketitle
\begin{abstract}
Many innovative software engineering tools appear at the field's premier venues, the 
International Software Engineering Conference (ICSE) and the 
Foundations of Software Engineering (FSE).
But what happens to these tools after they were presented?
In this paper, we spend 10,000 hours %update with real number 
trying to obtain, download, use, and repackage 150 %update
tools from ICSE and FSE's tool demonstration tracks.
Our results enumerate the practical and accidental reasons that
software engineering tools fail to work over time,
and provide practical implications for creating lasting tools.
\end{abstract}


%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002944.10011123.10010912</concept_id>
<concept_desc>General and reference~Empirical studies</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[300]{General and reference~Empirical studies}

\printccsdesc

\keywords{Software engineering tools; replication}

\section{Introduction}

Sofware engineering research seeks to better
understand software and how it is built and constructed.
While such understanding in isolation can be insightful,
ultimately a substantial amount of such research 
aims to impact the practice of software engineering.
To do so, researchers can create recommendations
for new software engineering practices, can 
create educational techniques and materials, 
and can create tools.

Arguably creating new tools is the most common
way that sofware engineering researchers
attempt to influence practice.
% evidence? would be good to see what the primary contributions are of a recent ICSE or FSE?
Broadly speaking, tools are software that can
help design and build software.
Examples include a tool that helps mobile application
developers choose which devices to target~\cite{prada},
a tool that checks the use of locks in multithreaded programs~\cite{ernst},
and a tool that creates code from natural language text~\cite{desai}.

While papers describe tools in software engineering venues,
there are several reasons why software engineering researchers 
should make the tools themselves available.
First, the full details of how the tool works, both in terms of its internals
and from an end-user perspective, may not be clear from the paper.
Second, making the tools available can help pracitioners try and adopt
the tools in their work.
Third, it helps facilitate reproducibility by enabling future researchers
to perform studies with the original tools.
Finally, it helps the advancement of the field by allowing others to build on 
existing tools, rather than re-buiding them from scratch.

Despite the benefits of making tools available, in this paper
we catalog the practical difficulties in doing so.
We describe a study that examined the tools presented at the 
premier venues for software engineering research over the 
past several years.
As part of a graduate university course on software engineering, 
we spent 10,000 hours trying to obtain, download, use
and repackage tools from the International Conference
on Sofware Engineering (ICSE) and the Symposium on the Foundations
of Software Engineering (FSE).
In doing so, we make the following three main 
contributions in this paper:

\begin{itemize}
  \item A study that evaluates the difficulty in getting tools 
  		working across a variety of software engineering research.
  \item A synergistic course project for graduate software engineering students 
		that gives students meaningful educational value \emph{and}
		provides the research community value.
  \item XXX existing tools repackaged in automatically-built virtual machines
  		to make it easier for others to use these tools.
\end{itemize}

\section{Related Work}

timeliness

General scientific interest in reproducibility.
How it fits with other Rs.
State of practice.

Software reproducibility outside SE.
Systems~\cite{collberg2016repeatability,proebsting2015repeatability}

Others~\cite{kovacevic2007encourage,vandewalle2009reproducible,stodden2009enabling,klein2012run}.


Arguably as SE researchers we should be the best!

Other fields:
- Data science (doing better - http://zenodo.org)
- MPC journal requires code submission (tarball)
- In general, Math not doing a lot with code sub submissions
- Security, should be able to do VM, but don't (but see Will's paper)
- HPC doesn't (and maybe can't)
- RTC is starting to do it, but maybe shouldn't

`` We argue that, with some exceptions, anything less than the release of source programs is intolerable for results that depend on computation.''~\cite{ince2012case}.

Constant worry is protecting IP in security and HPC

Repeatability in AI-SE: ``depends on who does it''
Reproducibility assessment for 2 papers, plus reproducibility overview~\cite{gonzalez2012reproducibility}


While no studies of software reproducibility in our field,
practical interest.

Artifact evaluation committees. (SIGPLAN, where else?)


\section{Research Questions}

Henceforth, we will simply say \textit{tool}
to refer to software engineering tools presented at
the International Conference on Software Engineering
or Foundations of Software Engineering in their
respective tool demonstration tracks.

\begin{enumerate}
  \item How much effort is required to get tools to work?
  \item What are the barriers to get tools to work?
  \item How much effort is required to get tools to work in virtual machines?
  \item What are the barriers to get tools to work in virtual machines?
  \item To what extent is this study practical to implement in a classroom context?
\end{enumerate}

\section{Course Description}

We conducted the study described in this paper as 
part of a graduate software engineering course
in the Computer Science department at 
North Carolina State University.
The department has about 200 PhD students and 450
MS students in its graduate program.
While graduate students are not required to
take the course, it is one of seven core systems
courses, from which students must take one course.
The department does have a specialty MS degree
track in software 
engineering,\footnote{\url{https://www.csc.ncsu.edu/academics/graduate/degrees/se.php}}
which does require this course.

Course content covers software engineering processes,
software architecture, design patterns, software security,
verification and validation, estimation, project managment,
requirements, certification, and formal 
methods.\footnote{Syllabus: \url{TODO}}
Apart from the course content, involving lectures and
a final exam, the other
major component of the course is the project.
Next, we describe the project for this course 
in prior offerings of the course (Section~\ref{sec:priorProj})
and in the offering described in this paper (Section~\ref{sec:thisProj}).

\subsection{Prior Course Project and Criticism}

%TODO experience report, rather than study? action research?

In prior offerings of the course,
students were essentially given two project offerings.
In one version, students could create
a software engineering tool, such as a plugin for Eclipse.
In the other version, students chose several existing,
similar software engineering tools, and applied them
to open source software, then reflected 
on what they learned about the tools and the 
projects.
Most students opted for the second version.
In both cases, students were required to write up their results.
This project is similar to a course project
assigned by David Notkin at the 
University of Washington.\footnote{\url{https://courses.cs.washington.edu/courses/cse503/}}

After offering this project to students for 
several years, the instructor recognized several
problems the way he had executed it:

\begin{itemize}  
  \item The course did not have enough time to teach students
  		technical writing skills, and thus final papers were 
  		of poor quality, on average. Moreover, while technical
  		communication is a course objective, other types of
  		communication would likely be more valuable to most
  		students, who are non-thesis and industry-focused.   		 
  \item Students had limited exposure to state-of-the-art
  		tools; the tools they chose to study were typically
  		quite basic.
  \item Students appeared to rarely gain technical skills 
  		during the project.  
  \item Most students were not doing \emph{novel} work; each semester,
  		different students wrote similar reports on similar tools,
  		which had no value beyond their educational value. 
\end{itemize}

While the last point may seem odd -- why would a course project need
value beyond its educational value? -- it's not unusual for 
some software enginering courses to have added value,
such as contributing to open source projects~\cite{pedroni2007open,meneely2008rose}.
In the case of the present course, the instructor thought 
that such system development would not be useful to most students
in the course, who typically come in with 1 to 2 years of 
industrial software engineering experience. 

\subsection{New Course Project}

In Fall of 2015, the instructor changed the course project
to allieviate the problems described in the last subsection.
In short, student teams were assigned tools described in a 
a prior research paper at ICSE or FSE, the premier 
venues for software engineering research.
Students were required to obtain the tools, get them running,
and redistribut them.

The instructor chose tool demonstration papers, rather than
full techncial papers, for practical reasons.
Full technical papers may not present a tool; for 
instance, a purely qualitative study that reports on 
empirical findings may have no software to go along with it.
In contrast, tool demo papers almost certainly had a working
tool when the paper was presented at a conference. 

There were several learning goals of the course project:

\begin{itemize}
  \item Gain deep experience with several state-of-the-art
  		software enginering tools, and broad overview of many others;
  \item Effectively read research papers;
  \item How to build virtual machines that contain custom
  		software;
  \item How to script virtual machine creation; and
  \item Oral communication skills. 
\end{itemize}

In the remainder of this section, we describe project
activities, requirements, and deliverables.

\subsubsection{Team Formation, Tool Selection, and Tool Assignment}

\subsubsection{Obtaining Tools}

\subsubsection{Getting the Tools Working}

\subsubsection{Presenting the Tools}

\subsubsection{Getting the Tools Working in a Virtual Machine}

\subsubsection{Building the Virtual Machine Automatically}

\section{Procedure}

No cost, but demos ok. (How many did this happen with?)

Tools where tool could convievably be put into a virtual machine. How many didn't fit?

\section{Results}

\subsection{RQ1 and RQ2}

\subsubsection{Effort}

Average person-hours per tool, distribution (min, max, box plot)

Time invested in evaluating non-working tools.

\subsubsection{Challenge: Tool Cannot Be Obtained}

What percent of tool links were dead?
What percent of tools said they were available in the paper, but the tool could not be obtained?
What percent of tools were being planned to be commercialized? What were actually commercial?
What percent of tools could we use if we had paid for them?

\subsubsection{Challenge: Disappearing Tools}

One author said tool just doesn't exist anymore.

Another author had to dig tool out of long term archive.

Several authors (what percent?) has tools hosted on Google code, even though it was dying.
Did we save 'em?

\subsubsection{Challenge: Author non-responsive}

%TODO: look at righthand column for tool; indications of why tools not working?

\subsubsection{Challenge: Technical Difficulties}

\subsubsection{Challenge: Inconsistencies}

One tool required to different VMs because two features needed different prereqs.

Some tools versioned differently.

\subsection{RQ3 and RQ4}


\subsubsection{Challenge: Tool Licensing}

University grey area.

\subsubsection{Challenge: Technology Stack Licensing}

\subsubsection{Challenge: Author Doesn't Want Redistribution}

Even when tool is available

\section{Conclusions}

Some other things.

%ACKNOWLEDGMENTS are optional
%\section{Acknowledgments}


\bibliographystyle{abbrv}
\bibliography{references}

\end{document}
